Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-14 paper/main.tex
Added table references and QA on choosing the implementations

\addcontentsline{toc}{chapter}{\listfigurename} % Manual, because report style
\listoffigures

@@

\begin{acronym}
\acro{AES}{Advanced Encryption Standard}
\acro{API}{Application programming interface}
\acro{CEB}{Capability Extension Block}
\acro{FEC}{Forward Error Correction}
\acro{LAFS}{Least-Authority Filesystem}
\acro{NIST}{National Institute of Standards and Technology}
\acro{RAM}{Random Access Memory}
\acro{RAID}{Redundant Array of Independent Disks}
\acro{SHA}{Secure Hash Algorithm}
\acro{SSE2}{Streaming SIMD Extensions 2}
\acro{SSSE3}{Supplemental Streaming SIMD Extensions 3}
\acro{SUPERCOP}{System for Unified Performance Evaluation Related to
Cryptographic Operations and Primitives}
\acro{UEB}{URI Extension Block}
\end{acronym}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.9\columnwidth]{Tahoe-hashes.pdf}
    \caption{Tahoe-LAFS: Example of hashing operations.}
    \label{fig:tahoehashing}
    \emph{Figure based on
     \href{http://tahoe-lafs.org/source/tahoe/trunk/docs/specifications/CHK-hashes.svg}
     {CHK-hashes.svg from tahoe-lafs.org}}
     %TODO: Footnote with full URL using footnotemark
\end{figure}

@@

\subsection{Cython}
Cython\footnote{\url{http://www.cython.org}} is a language for writing Python
extensions in a language that closely resembles the Python language itself.
Basically what Cython does is to parse cython files and generate C source files
that utilises the Python C-API. Afterwards the generated source files can be
compiled as if they were written directly in C. A small performance tradeoff is
to be expected from this, due to the extra layer of abstraction.

@@

@@

\appendix
\appendixpage
\addappheadtotoc

>>>>

\addcontentsline{toc}{chapter}{\listfigurename} % Manually add to ToC
\listoffigures

@@

\begin{acronym}
\acro{AES}{Advanced Encryption Standard}
\acro{API}{Application programming interface}
\acro{CEB}{Capability Extension Block}
\acro{FEC}{Forward Error Correction}
\acro{GCC}{GNU Compiler Collection}
\acro{KAT}{Known Answer Test}
\acro{LAFS}{Least-Authority Filesystem}
\acro{NIST}{National Institute of Standards and Technology}
\acro{RAM}{Random Access Memory}
\acro{RAID}{Redundant Array of Independent Disks}
\acro{SHA}{Secure Hash Algorithm}
\acro{SSE2}{Streaming SIMD Extensions 2}
\acro{SSSE3}{Supplemental Streaming SIMD Extensions 3}
\acro{SUPERCOP}{System for Unified Performance Evaluation Related to
Cryptographic Operations and Primitives}
\acro{UEB}{URI Extension Block}
\end{acronym}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.9\columnwidth]{Tahoe-hashes.pdf}
    \caption{Tahoe-LAFS: Example of hashing operations.}
    \label{fig:tahoehashing}
    \emph{Figure based on
     \href{http://tahoe-lafs.org/source/tahoe/trunk/docs/specifications/CHK-hashes.svg}
     {CHK-hashes.svg from Tahoe-LAFS documentation}}
     %TODO: Footnote with full URL using footnotemark
\end{figure}

@@

\subsection{Cython}
Cython\footnote{\url{http://www.cython.org}} is a language for writing Python
extensions in a language that closely resembles the Python language itself.
Basically what Cython does is to parse Cython files and generate C source files
that utilises the Python C-API. Afterwards the generated source files can be
compiled as if they were written directly in C. A small performance trade-off is
to be expected from this, due to the extra layer of abstraction.

@@

While the official \ac{NIST} \ac{SHA}-3 second round submissions contain both
a reference version and different optimized versions of the candidates, it does not
appear to be updated since the submission deadline on September 15, 2009. They
also do not contain any benchmarking utility which could be used to decide on
the best implementation for a particular platform or architecture. \ac{SUPERCOP}
on the other hand, provides both, in combination with results stating which
compiler arguments gives the best performance. On the downside, the
\ac{SUPERCOP} \ac{API} only specifies the \texttt{crypto\_hash()} function and
not an \texttt{update()} function which Tahoe-\ac{LAFS} is dependent on using.

Since Tahoe-\ac{LAFS} is using \ac{SHA}-256 internally, we only test \ac{SHA}-3
functions with 256-bit output in our implementation. The results of \ac{SHA}-3
256-bit functions and \ac{SHA}-256 benchmarking in \ac{SUPERCOP} can be seen in
tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8}. The lower the numbers, the faster the algorithms
performed in the test.

We then chose the fastest implementation of each candidate that conforms to the
following criteria:
\begin{enumerate}
  \item The implementation must have an \ac{API} defined in C.
  \item The implementation must include a working \verb update() function.
  \item The implementation must not use assembly that can not be made
    position independent by \ac{GCC}.
  \item The implementation should conform to the \acp{KAT} specified in the
    \ac{NIST} submission package, or later updates by the author.
\end{enumerate}

% TODO: Add some lines that give reasons for the criteria above.

@@

% Uncomment to enable appendices.
%\appendix
%\appendixpage
%\addappheadtotoc
